SST_patterns

### 2019-08-31 SST_patterns.Rmd
updated

```{r}
load("Data/site_list_sub.Rdata")
load("Data/SACTN_US.RData")
load("Data/site_pixels.RData")
```

@@

```{r}
bbox <- data.frame(BC = c(-35, -25, 15, 20), # Benguela Current
                   CC = c(25, 35, 340, 355), # Canary Current
                   CalC = c(35, 45, 225, 240), # California Current
                   HC = c(-17.5, -7.5, 275, 290), # Humboldt Current
                   row.names = c("latmin", "latmax", "lonmin", "lonmax"))

OISST.dir <- "/home/amieroh/Documents/Data/Datasets/OISSTv2/daily/netCDF/avhrr-only"
OISST.csv.dir <- "/home/amieroh/Documents/OISST_subset"

#          1         2
# 1234567890123456789012345
# avhrr-only-v2.19810901.nc

# function to extract the dims and data from OISST netCDFs
read_nc <- function(ncFile, region = region, csvDir = csvDir) {
  coords <- bbox[, region]
  nc <- nc_open(ncFile)
  pathLen <- nchar(OISST.dir) + 1 # to account for the "/" that needs to be inserted
  fNameStem <-
    substr(ncFile, pathLen + 1, pathLen + 13)
  fDate <- substr(ncFile, pathLen + 15, pathLen + 22)
  LatIdx <- which(nc$dim$lat$vals > coords[1] & nc$dim$lat$vals < coords[2])
  LonIdx <- which(nc$dim$lon$vals > coords[3] & nc$dim$lon$vals < coords[4])
  sst <- ncvar_get(nc,
                   varid = "sst",
                   start = c(LonIdx[1], LatIdx[1], 1, 1),
                   count = c(length(LonIdx), length(LatIdx), 1, 1)) %>%
    round(4)
  dimnames(sst) <- list(lon = nc$dim$lon$vals[LonIdx],
                        lat = nc$dim$lat$vals[LatIdx])
  nc_close(nc)
  sst <-
    as.data.table(melt(sst, value.name = "temp"), row.names = NULL) %>%
    mutate(t = ymd(fDate)) %>%
    na.omit()
  fwrite(sst,
         file = paste(csvDir, "/", region, "-", fNameStem, ".", strtDate, "-", endDate, ".csv", sep = ""),
         append = TRUE, col.names = FALSE)
  rm(sst)
}

# the list of files
ncList <- list.files(path = OISST.dir, pattern = "*.nc", full.names = TRUE, include.dirs = TRUE)
strtDate <- str_sub(ncList[1], start = 15, end = 22)
endDate <- str_sub(ncList[length(ncList)], start = 15, end = 22)

# apply the function
system.time(llply(ncList, read_nc, region = "BC", csvDir = OISST.csv.dir, .parallel = TRUE))
# system.time(llply(ncList, read_nc, region = "CC", csvDir = OISST.csv.dir, .parallel = TRUE))
# system.time(llply(ncList, read_nc, region = "CalC", csvDir = OISST.csv.dir, .parallel = TRUE))
# system.time(llply(ncList, read_nc, region = "HC", csvDir = OISST.csv.dir, .parallel = TRUE))

```

>>>>

```{r}
load("Data/site_list_sub.Rdata")
load("Data/SACTN_US.RData")
load("Data/site_pixels.RData")
load("Data/OISST.RData")
```

@@

```{r}
# bbox <- data.frame(BC = c(-35, -25, 15, 20), # Benguela Current
#                    CC = c(25, 35, 340, 355), # Canary Current
#                    CalC = c(35, 45, 225, 240), # California Current
#                    HC = c(-17.5, -7.5, 275, 290), # Humboldt Current
#                    row.names = c("latmin", "latmax", "lonmin", "lonmax"))
# 
# OISST.dir <- "/home/amieroh/Documents/Data/Datasets/OISSTv2/daily/netCDF/avhrr-only"
# OISST.csv.dir <- "/home/amieroh/Documents/OISST_subset"
# 
# #          1         2
# # 1234567890123456789012345
# # avhrr-only-v2.19810901.nc
# 
# # function to extract the dims and data from OISST netCDFs
# read_nc <- function(ncFile, region = region, csvDir = csvDir) {
#   coords <- bbox[, region]
#   nc <- nc_open(ncFile)
#   pathLen <- nchar(OISST.dir) + 1 # to account for the "/" that needs to be inserted
#   fNameStem <-
#     substr(ncFile, pathLen + 1, pathLen + 13)
#   fDate <- substr(ncFile, pathLen + 15, pathLen + 22)
#   LatIdx <- which(nc$dim$lat$vals > coords[1] & nc$dim$lat$vals < coords[2])
#   LonIdx <- which(nc$dim$lon$vals > coords[3] & nc$dim$lon$vals < coords[4])
#   sst <- ncvar_get(nc,
#                    varid = "sst",
#                    start = c(LonIdx[1], LatIdx[1], 1, 1),
#                    count = c(length(LonIdx), length(LatIdx), 1, 1)) %>%
#     round(4)
#   dimnames(sst) <- list(lon = nc$dim$lon$vals[LonIdx],
#                         lat = nc$dim$lat$vals[LatIdx])
#   nc_close(nc)
#   sst <-
#     as.data.table(melt(sst, value.name = "temp"), row.names = NULL) %>%
#     mutate(t = ymd(fDate)) %>%
#     na.omit()
#   fwrite(sst,
#          file = paste(csvDir, "/", region, "-", fNameStem, ".", strtDate, "-", endDate, ".csv", sep = ""),
#          append = TRUE, col.names = FALSE)
#   rm(sst)
# }
# 
# # the list of files
# ncList <- list.files(path = OISST.dir, pattern = "*.nc", full.names = TRUE, include.dirs = TRUE)
# strtDate <- str_sub(ncList[1], start = 15, end = 22)
# endDate <- str_sub(ncList[length(ncList)], start = 15, end = 22)
# 
# # apply the function
# system.time(llply(ncList, read_nc, region = "BC", csvDir = OISST.csv.dir, .parallel = TRUE))
# # system.time(llply(ncList, read_nc, region = "CC", csvDir = OISST.csv.dir, .parallel = TRUE))
# # system.time(llply(ncList, read_nc, region = "CalC", csvDir = OISST.csv.dir, .parallel = TRUE))
# # system.time(llply(ncList, read_nc, region = "HC", csvDir = OISST.csv.dir, .parallel = TRUE))
# 
# # Loading the data
# BC_avhrr_only_v2_Document_Document <- read_csv("~/Documents/OISST_subset/BC-avhrr-only-v2.Document-Document.csv" )
# names(BC_avhrr_only_v2_Document_Document)<-c("lon","lat", "temp", "date")
# 
# # Saving the data
# save(BC_avhrr_only_v2_Document_Document, file = "Data/OISST.RData")
```
